Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
Figure 4 disp ready

# Figure x - average dispersal and dispersion per run

@@

# ggsave2(filename = "Ch1_movement_rates/Figures/disp_plot.png")

@@

### With the real data

```{r}
disp_r_df %>%
  group_by(., model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> pr_dispersion

disp_r_df %>%
  group_by(., model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(y = av.disp, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> pr_dispersal

plot_grid(pr_dispersal, pr_dispersion)
```

>>>>

# Figure 4 - average dispersal and dispersion per run

@@

# ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")

@@
